msAggr_seurat-v1

### 2021-06-14 msAggr_AnalysisCode/msAggr_seurat-v1.Rmd
Seuratv4 pipeline continuance

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
```
store session info
```{r}
sink("msAggr_seurat-v1.20210608")
sessionInfo()
sink()
```

@@

```{r}
seurat.object[["percent.mt"]] <- PercentageFeatureSet(seurat.object, pattern = "^mt-")
VlnPlot(seurat.object, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0, fill.by = 'orig.ident')
```

@@

@@

```{r}
seurat.object <- 
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
```
store session info
```{r}
sink("msAggr_seurat-v1.20210608")
sessionInfo()
sink()
```

@@

Clean up to free memory

```{r}
remove(seurat.object.data)
```

Add mitochondrial metadata and plot some basic features
```{r}
seurat.object[["percent.mt"]] <- PercentageFeatureSet(seurat.object, pattern = "^mt-")
VlnPlot(seurat.object, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0, fill.by = 'orig.ident')
```

@@

### Save progress

```{r}
save.image(file = paste0(projectName, '.RData'))
```

@@

```{r}
seurat.object <- RunPCA(seurat.object, features = VariableFeatures(object = seurat.object))
```

```{r fig.width=4, fig.height=4}
VizDimLoadings(seurat.object, dims = 1:6, nfeatures = 10, reduction = "pca", ncol = 2)
```

DimPlot colored by orig.ident
```{r}
DimPlot(seurat.object, reduction = "pca", group.by = "orig.ident")
```

Let's put in a concerted effort to pick the right dimensionality using the newest software

```{r}
seurat.object <- JackStraw(seurat.object, num.replicate = 100, dims = 40) #runs ~50 min
seurat.object <- ScoreJackStraw(seurat.object, dims = 1:40)
save.image(paste0(projectName, ".RData"))
```

Draw dim.reduction plots

```{r}
# plot1 <- JackStrawPlot(seurat.object, dims = 1:50)
```
```{r, figures-side, fig.show='hold', out.width="50%"}
ElbowPlot(seurat.object, ndims = 50)
percent.variance(seurat.object@reductions$pca@stdev)

```
Number of PCs describing X% of variance

```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
paste0("Num pcs for 80% variance:", length(which(cumsum(tot.var) <= 80)))
paste0("Num pcs for 85% variance:", length(which(cumsum(tot.var) <= 85)))
paste0("Num pcs for 90% variance:", length(which(cumsum(tot.var) <= 90)))
paste0("Num pcs for 95% variance:", length(which(cumsum(tot.var) <= 95)))

36 PCs describe 95% percent of variance, but one of the earlier critiques was that too many dimensions were included. Best way to deal with this is probably to try a couple of different ones. Let's start with 36 because I dare to rebel.

```{r}
seurat.object <- FindNeighbors(seurat.object, dims = 1:36)
seurat.object <- FindClusters(seurat.object, resolution = 0.5)
```

Generate UMAP data
```{r}
seurat.object <- RunUMAP(seurat.object, dims = 1:36) # took < 1 min
```

Plot the results
```{r}
DimPlot(seurat.object, 
				reduction = "umap"
				) + ggtitle("msAggr dim36 res0.5")

```{r}
DimPlot(seurat.object,
				reduction = "umap", 
				group.by = "orig.ident"
				) + ggtitle("msAggt dim36 orig.ident")
```

```{r}
saveRDS(seurat.object, file = "msAggr_dim36.rds")
```

Not a fan of how "swoopy" it looks. Could be to many dimensions? May as well try 90%

```{r}
seurat.object <- FindNeighbors(seurat.object, dims = 1:24)
seurat.object <- FindClusters(seurat.object, resolution = 0.5)
seurat.object <- RunUMAP(seurat.object, dims = 1:24)
```

Plot the results
```{r}
DimPlot(seurat.object, 
				reduction = "umap"
				) + ggtitle("msAggr dim24 res0.5")

```{r}
DimPlot(seurat.object,
				reduction = "umap", 
				group.by = "orig.ident"
				) + ggtitle("msAggt dim24 orig.ident")
```

```{r}
saveRDS(seurat.object, file = "msAggr_dim24.rds")
```

24 vs 36 dimensions doesn't seem to make that much difference RE overall relationships. Should probbaly create two separate objects and try a few plotting methods.
